Explaining Amsterdam House Prices with Greenness

### 2023-04-11 README.Rmd
readme

@@

![Overview of study area](Paper/figures/Methods.jpg)

@@

The used data regarding the Public Amenities can be found in the [/data/Amsterdam/ folder](https://github.com/JitseRuurd/Amsterdam_Urban_Green/tree/main/data/Amsterdam) and partly in [the 1.c Data Enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R).

@@

Lastly, the Remote Sensing data was extracted with below code in the [1.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb), and was inspired from the Planetary computer:

@@

To then use the data for the analysis, the [pre-processing R script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1a.%20Pre-processing.R) provides the code to geocode the adresses from the Funda.nl data to latlon column.

@@

>>>>

The goal of this research was to extimate the effect of greenness on house prices in Amsterdam.

@@

![Overview of methods](Paper/figures/Methods.jpg)

@@

The used data regarding the Public Amenities can be found in the [/data/Amsterdam/ folder](https://github.com/JitseRuurd/Amsterdam_Urban_Green/tree/main/data/Amsterdam) and partly in the [1.c Data Enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R).

@@

Lastly, the Remote Sensing data was extracted with below code in the [1b.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb), and was inspired from the Planetary computer:

@@

The data enhancement for the public amenities was performed in the [1.c Data enrichment script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1c.%20Data%20enrichment.R). The steps within this script consist of finding the nearest facility for every house regarding every public amenity included.

To use the Funda.nl data for the analysis, the [pre-processing R script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1a.%20Pre-processing.R) provides the code to geocode the adresses from the Funda.nl data to latlon column. Below chunk shows this code:

@@

The pre-processing of the Remote sensing data consists of the computation of the NDVI value. This was done in the [1b.Pre-Processing script](https://github.com/JitseRuurd/Amsterdam_Urban_Green/blob/main/1b.%20Pre-Processing.ipynb) with below code:
```{python eval = F}

ndvi = xrspatial.multispectral.ndvi(data['nir'], data['red'])

ndvi.values[ndvi.values < 0] = 0
```
Note that negative NDVI values where set to 0.

## Hedonic pricing approach

With the enhanced data, several models where used to estimate the effect of greenness on the house prices in Amsterdam.

First, an OLS model was used:

```{r eval = F}
equation <- price_m2 ~ bedroom + bathroom + living_area + house_age + tram_dist + metro_dist + train_dist + ndvi300 + centre_dist + zuid_dist + shops_dist + school_dist

#OLS
model <- lm(equation, 
            data = funda_data)
```

After checking the Linear regression assumptions (results stated in the paper), an Geographically Weighted Regression (GWR) model was used as implemented below:

```{python eval = F}
#Run basic GWR in parallel mode
gwr_selector = Sel_BW(b_coords, b_y, b_X, kernel='bisquare')
gwr_bw = gwr_selector.search(pool = pool, criterion = "AIC") 
print(gwr_bw)
gwr_results = GWR(b_coords, b_y, b_X, gwr_bw, kernel="bisquare").fit(pool = pool)
```

## Results

With the final GWR model, the results of the analysis were created. The main output of the analysis was the significant coefficient map shown below.

![Overview of results](Paper/Figures/Economic_Value_Urban_Green_clip.png)

The interpetation and conclusion of this plot is stated in chapter 3 and 4 of the report, respectively.
